%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% File: utthesis2.doc, version 2.0jab, February 2002
%%%
%%% Based on: utthesis.doc, version 2.0, January 1995
%%% =============================================
%%% Copyright (c) 1995 by Dinesh Das.  All rights reserved.
%%% This file is free and can be modified or distributed as long as
%%% you meet the following conditions:
%%%
%%% (1) This copyright notice is kept intact on all modified copies.
%%% (2) If you modify this file, you MUST NOT use the original file name.
%%%
%%% This file contains a template that can be used with the package
%%% utthesis.sty and LaTeX2e to produce a thesis that meets the requirements
%%% of the Graduate School of The University of Texas at Austin.
%%%
%%% All of the commands defined by utthesis.sty have default values (see
%%% the file utthesis.sty for these values).  Thus, theoretically, you
%%% don't need to define values for any of them; you can run this file
%%% through LaTeX2e and produce an acceptable thesis, without any text.
%%% However, you probably want to set at least some of the macros (like
%%% \thesisauthor).  In that case, replace "..." with appropriate values,
%%% and uncomment the line (by removing the leading %'s).
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%
%% This file, and the corresponding tcdthesis.sty the accompanied it, have
%% been modified for the M.Sc. styles used in Trinity College, Dublin
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper, 12pt, oneside]{report}         %% LaTeX2e document.
\usepackage{algorithm,algorithmic}
\usepackage {tcdthesis}              %% Preamble.
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{array}

\mastersthesis                     %% Uncomment one of these; if you don't
% \phdthesis                         %% use either, the default is \phdthesis.

\thesisdraft                       %% Uncomment this if you want a draft
                                     %% version; this will print a timestamp
                                     %% on each page of your thesis.

\leftchapter                       %% Uncomment one of these if you want
%\centerchapter                      %% left-justified, centered or
% \rightchapter                      %% right-justified chapter headings.
                                     %% Chapter headings includes the
                                     %% Contents, Acknowledgments, Lists
                                     %% of Tables and Figures and the Vita.
                                     %% The default is \centerchapter.

% \singlespace                       %% Uncomment one of these if you want
\oneandhalfspace                   %% single-spacing, space-and-a-half
% \doublespace                       %% or double-spacing; the default is
                                     %% \oneandhalfspace, which is the
                                     %% minimum spacing accepted by the
                                     %% Graduate School.

\renewcommand{\thesisauthor}{Salil Ajgaonkar}            %% Your official TCD name.
\renewcommand{\thesismonth}{August}                  %% Your month of graduation.
\renewcommand{\thesisyear}{2018}                      %% Your year of graduation.
\renewcommand{\thesistitle}{Proof Of Concept for Opportunistic Security in MPLS Networks}            %% The title of your thesis; use mixed-case.
\renewcommand{\thesisauthorpreviousdegrees}{ B.E}  %% Your previous degrees, abbreviated; separate multiple degrees by commas.
\renewcommand{\thesissupervisor}{Stephen Farrell}      %% Your thesis supervisor; use mixed-case and don't use any titles or degrees.
% \renewcommand{\thesiscosupervisor}{}                %% Your PhD. thesis co-supervisor; if any.

% \renewcommand{\thesiscommitteemembera}{}
% \renewcommand{\thesiscommitteememberb}{}
% \renewcommand{\thesiscommitteememberc}{}
% \renewcommand{\thesiscommitteememberd}{}
% \renewcommand{\thesiscommitteemembere}{}
% \renewcommand{\thesiscommitteememberf}{}
% \renewcommand{\thesiscommitteememberg}{}
% \renewcommand{\thesiscommitteememberh}{}
% \renewcommand{\thesiscommitteememberi}{}


\renewcommand{\thesisauthoraddress}{25, Liffey Walk, North Lotts, Dublin 1}

\renewcommand{\thesisdedication}{XXXX}     %% Your dedication, if you have one; use "\\" for linebreaks.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% The following commands are all optional, but useful if your requirements
%%% are different from the default values in tcdthesis.sty.  To use them,
%%% simply uncomment (remove the leading %) the line(s).

\renewcommand{\thesisdegree}{Master of Science in Computer Science}  
                                     %% default is "DOCTOR OF PHILOSOPHY"
                                     %% for \phdthesis or "MASTER OF ARTS"
                                     %% for \mastersthesis.  Provide the
                                     %% correct FULL OFFICIAL name of
                                     %% the degree.
\renewcommand{\thesisdegreestream}{(Future Network Systems)}
                                     %% Default is empty. This is used on
                                     %% the title page of the thesis.

\renewcommand{\thesisdegreeabbreviation}{M.Sc.}
                                     %% Use this if you also use the above
                                     %% command; provide the OFFICIAL
                                     %% abbreviation of your thesis degree.
\renewcommand{\thesistype}{Dissertation}    %% Use this ONLY if your thesis type
                                     %% is NOT "Thesis" for \phdthesis
                                     %% or \mastersthesis.
                                     %% Provide the OFFICIAL type of the
                                     %% thesis; use mixed-case.

% \renewcommand{\thesistypist}{...}  %% Use this to specify the name of
                                     %% the thesis typist if it is anything
                                     %% other than "the author".

%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}                                  %% BEGIN THE DOCUMENT

\thesistitlepage                                  %% Generate the title page.

\thesisdeclarationpage                %% Generate the declaration page.

\thesispermissionpage                 %% Generate the copyright permission page

%\thesisdedicationpage                             %% Generate the dedication page.

\begin{thesisacknowledgments}                     %% Use this to write your
First and foremost I would like to thank my thesis advisor Dr. Stephen Farrell of the School of Computer Science and Statistics at Trinity College Dublin whose guidance and expertise has given me wealth of knowledge which I shall forever carry with me.

I would also like to acknowledge Dr. Donal E. O'Mahony of the School of Computer Science and Statistics at Trinity College Dublin as the second reader of this thesis, and I am gratefully indebted to his very valuable comments on this thesis.

Finally, I would like to express my extreme gratitude to my parents without whose support I would have never been able to be the man I am today. Who constantly encouraged and pushed me to be the best I can be and have been a source of unfailing support and encouragement throughout my years of study. This accomplishment would not have been possible without them. Thank you.

%% acknowledgments; it can be anything
\end{thesisacknowledgments}                       %% allowed in LaTeX2e par-mode.

\begin{thesisabstract}                          %% the abstract for your thesis

Multiprotocol Label Switching (MPLS) is a high performance packet switching technology which supports packet switching for multiple protocols and access technologies. It is a switching technology that redirects data based on short label paths rather than an IP table lookup. Each Label Switched Router in the MPLS network has a table that tells the router how to handle and redirect specific types of data. This helps the router to handle data in a consistent fashion while maintaining flexibility for traffic engineering at the same time.

MPLS provides networking corporations and government high speed and reliable data transfer over geographically dispersed sites while maintaining flexibility and high bandwidth data exchange. It is very easy to scale and can be efficiently tuned to meet various service level requirements. it is primarily used to provide Virtual Private Network (VPN) services for corporations who wish to transfer private data over a public network.

Such a heavy reliance on MPLS by big companies and the general public to manage their data means that any forms of network attacks often have the potential to disrupt vital everyday operations. Attacks ranging from data theft to denial of service if successful may lead to severe damages to the service provider as well as the owner of the data.

Earlier work conducted by the Internet Engineering Task Force (IETF) have analyzed the various vulnerabilities and security threats that affect the MPLS technology and have drafted a potential resolution to some of the security issues. This work proposed the implementation of Opportunistic Security in the MPLS network using payload encryption to encrypt the underlying application data and protocols headers using symmetric key encryption between end to end or hop by hop Label Switching Routers (LSRs) on an MPLS Label Switched Path (LSP).

This thesis describes the proof of concept for this proposed solution by implementing it on an experimental controlled environment and measuring its effects on the overall functionality and features of the presently running MPLS technology, the results of which should give an idea regarding the feasibility of the solution in practical commercial network in the world.  
\end{thesisabstract}

\begin{thesissummary}                           %% The summary page for your thesis

MPLS is a network routing technology which uses circuit switching and packet switched network technologies to support data routing for multiple protocols. It is a protocol independent and highly scalable technology whose flexibility enables efficient utilization of network resources resulting in high quality of service at low cost. MPLS relies on the use of fixed bytes of data that represent as labels for routing decisions. These labels are pushed on top of a data packet at the ingress (entering) switch of an MPLS network. All the succeeding Label Switching Routers (LSRs) in the MPLS cloud lookup these labels to appropriately route the data to the correct destination. The path to the destination is pre-configured in the LSR's label lookup table rather than an IP routing table. This avoids any complex lookups or reading long network addresses and implementation of longest match algorithms. Once the MPLS packet reaches the egress (exiting) switch of the MPLS network, the MPLS label is popped off and the data packet is then transmitted as a regular original packet along the succeeding switches. The LSRs between the ingress and the egress switch of the MPLS cloud also have the capability of pushing and popping off the MPLS labels on the data packet to efficiently engineer the network traffic.

	Networking corporations and service providers leverage this flexibility to scale their network services. Using the advantages of MPLS they are able to run high bandwidth applications over seamless IP based networks that connect multiple, remote site \cite{grayson2009analysis}. The reliance on MPLS VPNs by corporations and government agencies means that attacks ranging from intercepting sensitive data to disrupting data, voice and multimedia services can significantly impact vital operations \cite{mpls-os-internet-draft}.

	Previously in MPLS, data security in the MPLS network mainly relied on just three features: \\
    1) Physical isolation of MPLS networks that ensured interception of MPLS traffic was not possible. \\
    2) Higher-layer protocol security such as IPsec which had been used whenever a particular flow has determined that security was desirable \cite{grayson2009analysis}.\\
    3) Layer 2 protocol security like MACSec where security was implemented on a hop by hop basis between devices connected on the Ethernet. 
    However these features have a number of vulnerabilities. The network is still vulnerable to network taps between links, misconfiguration of routers, data replication, at the same time users might not enable to implement end to end security in their applications \cite{grayson2009analysis}.
    
    To mitigate these vulnerabilities to some extent, the IETF drafted an Internet-draft titled "Opportunistic Security in MPLS Networks draft-ietf-mpls-opportunistic-encrypt-03" which proposed a novel idea of implementing Opportunistic Security (OS) in the currently existing MPLS implementations. The Internet draft suggested the implementation of opportunistic encryption of data payload which is held by the MPLS packet using symmetric key encryption. As the LSR's only rely on the information contained in the MPLS labels for routing, the contents of the MPLS packet are of no significance for the flow of traffic. Thus end-to-end or hop-by-hop encryption of the data payload of the MPLS packet by the LSRs may contribute to maintaining the confidentiality, integrity and authenticity of the data that flows through the MPLS network.
    
    This dissertation describes a way to implement this proposed experimental idea in a controlled environment by simulating the flow of traffic in an MPLS network in a virtual network and comparing the difference in performance between MPLS with the OS and MPLS without the OS. This will help validate or invalidate the proposed solution experimentally and further spread more light on its impact and feasibility on real world implementation.
    
    This experiment is carried out using an experimental network setup consisting of mininet as a virtualized network platform. On this virtual platform OpenVSwitch (OVS) virtual switches are setup which simulate the flow of network traffic through the virtual switches. The MPLS flows needed to configure the OVS switches are configured using OpenFlow Software Defined Networking (SDN) Technology. OpenFlow configures these OVS switches by installing flow rules to simulate the behavior of an MPLS switch. The Opportunistic Security feature in the MPLS is implemented by coding the symmetric key functionality into the existing OVS code base which would then be configured onto the OVS switches in the mininet network to simulate the behavior of the system with the OS. We then evaluated the performance of the system by measuring certain network performance metrics and compared them with the ones measured without the OS. This comparative analysis may help us understand the performance level of the OS in MPLS against MPLS without OS, if there are any room for improvements and its potential impact on practical implementation. 
 \end{thesissummary}


\tableofcontents                                  %% Generate table of contents.
\listoftables                                     %% Uncomment this to generate list of tables.
\listoffigures                                    %% Uncomment this to generate list of figures.

%%
%% Include thesis chapters here...
%%
  \include{1_StateOfTheArt}
  \include{2_Design}
  \include{4_Experiment}
  \include{5_Results}
  \include{6_FutureWork}
  \include{7_Conclusion}


% \begin{thebibliography}{ieee}                   %% Start your bibliography here; you can
% \bibliography{refs}                               %% also use the \bibliography command
% \end{thebibliography}                             %% to generate your bibliography.

\bibliographystyle{ieee}
\bibliography{refs}



\addcontentsline {toc}{chapter}{Appendices}       %% Force Appendices to appear in contents
\begin{appendix}
\include{appendix1}
% \include{appendix2}
\end{appendix}


%\addcontentsline {toc}{chapter}{Bibliography}     %% Force Bibliography to appear in contents


\end{document}                                    %% END THE DOCUMENT
